\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{multicol}
\usepackage{changepage} % for adjustwidth

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Rishav Roy} \\ \vspace{1pt}
    \small  
    \href{https://github.com/rishavbroy}{{github.com/rishavbroy}} $|$ 
    \href{mailto:roybrishav@gmail.com}{{roybrishav@gmail.com}} $|$
    \href{tel:19857893732}{+1-985-789-3732}
\end{center}

\begin{comment}
\vspace{-6mm}
\begin{center}
    Proven, driven, and organized researcher. Manages and executes at every stage of research over multiple projects. \\ Excels in graduate-level economics and mathematics. Strong, clear communicator and passionate collaborator.
\end{center}
\end{comment}
\vspace{-1mm}

\vspace{-6.5mm}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Wisconsin--Madison, B.S.}{Spring 2026}
      {\parbox[t]{0.65\textwidth}{Triple Major: Economics, Mathematics, and Data Science \\ \textnormal{\textbf{Recent GPA (since Summer 2024): 3.9} $|$ Overall GPA: 3.3}}}{Madison, WI}%\footnotesize{}
      \vspace{2mm}
    \resumeSubheading
      {Graduate-Level Coursework}{}{}{}
      \vspace{-5.5mm}
      \begin{multicols}{2}
      \begin{itemize}[label={}]
        \item PhD Macroeconomics I--II (MATLAB) \parbox[t]{0.5\textwidth}{\vspace{-0.8em} \footnotesize \underline{\textbf{\textit{Top scorer}} in PhD Macroeconomics II}}
        \item PhD Microeconomics I--II
        \item PhD Industrial Organization I--II (audit)
        \item PhD Econometrics I--II (Stata) \parbox[t]{0.5\textwidth}{\vspace{-0.8em} \footnotesize \underline{\textbf{\textit{Top scorer}} in PhD Econometrics II} in 18-cr. semester}
        \item Master’s-Level Measure \& Integration (Honors) \parbox[t]{0.5\textwidth}{\vspace{-0.9em} \footnotesize \underline{\textit{Top scorer}} of first half in 18-cr. semester}
      \end{itemize}
      \end{multicols}
      \vspace{-5mm}
    \resumeSubheading
      {Select Undergraduate Coursework}{}{}{}
      \vspace{-5.5mm}
      \begin{multicols}{2}
      \begin{itemize}[label={}]
          \item Data Science Programming I--II (Python, SQL)
          \item Introduction to Optimization (Julia)
          \item Machine Learning \& Classification (Python)
          \item Econometrics: AI \& Machine Learning (R)
          \item Foundation Models \& LLMs (Python)
          \item Real Analysis I--II (Honors)
      \end{itemize}
      \end{multicols}
  \resumeSubHeadingListEnd

%-----------RESEARCH-----------

\vspace{-9mm}

\begin{comment}
\section{Research Interests}
\hspace{2mm} Political Economy, Labor, Industrial Organization, Development, and Applied Econometrics
\vspace{-2.5mm}
\end{comment}
\begin{comment}
\section{Research Interests}
\hspace{2mm} Public Policy, Labor, Industrial Organization, Development, and Applied Econometrics
\vspace{-2.5mm}
\end{comment}


\vspace{1mm}

\section{Research Experience}
\resumeSubHeadingListStart
    \resumeSubheading{Escaping Inequality in India: The Role of English-Medium Instruction}{Spring 2025--Present}{Senior Thesis Paper (with feedback from Prof. Laura Schechter)}{}
    \resumeItemListStart

        \resumeItem{Built a district pseudo-panel ($N = 454$) merging 2007-08/2017-18 survey microdata and metadata, 35 Census 2001 language files, \& 2019-20 shapefiles to study EMI exposure on consumption growth with survey-weighted measures.}

        \resumeItem{Estimated district-level 2SLS with state-level clustered SEs, partial $F=39.20$. Documented endogeneity threats, spatial spillovers (Moran's $I$, Monte Carlo). Designed reusable IV generator to safely iterate 2SLS specifications.}
        %\resumeItem{Estimated district-level 2SLS with state-level clustered SEs. Verified relevance (partial $F=39.20$) of IV, the 2001 pop.-WA of mother tongues' linguistic distance  from Hindi. Documented endogeneity threats, spatial spillovers (Moran's $I$, Monte Carlo), ecological fallacy. Designed reusable IV generator to safely iterate 2SLS specifications.}

        \resumeItem{Estimated enrollment probit with design-based SEs, complex survey design (nested strata, lonely PSUs). Computed AME, delta-method SEs via autodiff. Rejected MCAR via logits, BH procedure. Mitigated systematic missingness.}
        %\resumeItem{Detected spatial autocorrelation via Moran's $I$, constructed spatial lags, \& prototyped spatial IV/GMM.}

        \resumeItem{Harmonized districts across renames/mergers/splits \& typos via multi-pass fuzzy joins (soundex, q-gram, etc.), canonicalization, \& 80 manual matches. Engineered data intake tools robust to OS-specific file-naming conventions.} % Identified duplicates driving multicollinearity.
       
        \resumeItem{Drafted 49-page paper in R Markdown with detailed replication notes, automated publication-quality maps/tables.}
    \resumeItemListEnd


    \resumeSubheading{Language Models as Measurement Instruments: Risks for Estimation}{Spring 2026--Present}{Independent Research Project (with feedback from Prof. Harold D. Chiang)}{}
    \resumeItemListStart
        \resumeItem{Formulated LM-generated measures as noisy proxies for central banks’ latent policy stance. Decomposed noise into error/leakage channels whose effects on downstream economic estimation I then experimentally isolated.}

        \resumeItem{Built reproducible Python codebase for World Central Banks corpus (380,200 sentences, 3,453 docs, 1996-2024): ingestion, measurement, aggregation, FE regressions with IMF/World Bank data, and automated tables/figures.}

        \resumeItem{Evaluated non-classical measurement error using 25,000 human-labeled sentences and entity masking, semantic perturbations, validation sample-size simulations, regressions predicting errors, and sensitivity to aggregation rules.}

        \resumeItem{Currently fine-tuning RoBERTa model while using a TF-IDF/logit baseline to benchmark and debug the pipeline. Will compare models by predictive performance, potential propagation of errors into macroeconomic estimation.}
        
    \resumeItemListEnd


    \resumeSubheading{Fast Inference for Large-$N$ Panel Quantile Regression \& Common Shocks}{Spring 2026--Present}{Research Project (with guidance from Prof. Harold D. Chiang)}{}
    \resumeItemListStart
        \resumeItem{Defined stochastic subgradient estimator for fixed-effects panel quantile regression under common shocks. Demonstrated $\sqrt{T}$-normality under full-period stochastic increments. Outlined Polyak-Ruppert averaging, online updating, and mini-batch rate conditions for $o_p(T^{-1/2})$ score residuals and stochastic approximation errors.}
        \resumeItem{Eliminated first-order effect of FE scores and $N$-dimensional incidental parameters via orthogonalized slope moment, yielding the Schur-complement Jacobian $\Gamma$ and identifying the common-shock variance component $\Sigma$.}
        \resumeItem{Developed proof strategy for first-order equivalence between one-step corrected SGD estimator and exact FEQR: asymptotically negligible KKT residuals imply $\sqrt{T}$-normality and valid $\Gamma^{-1}\Sigma\Gamma^{-1}$ sandwich inference.}

    \resumeItemListEnd

%\begin{comment}
    \resumeSubheading{Empirical Implications of Stochastic Hysteresis on Optimal Policy}{Fall 2025}{Independent Research Project  (with guidance from Prof. Job Boerma)}{}
    \resumeItemListStart
        \resumeItem{Derived observable proxies for \href{https://jobboerma.com/wp-content/uploads/policy_hysteresis.pdf}{Boerma et al. (2023)}'s Malliavin/Itô calculus given CRRA utilities, CRS, etc. to distinguish true hysteresis from persistence or long memory in macro, finance, and climate policy.}
        
        \resumeItem{Developed framework to falsify large class of Markov models (e.g., DSGE, VAR) using non-Markov time series. Assessed computational and identification tradeoffs of Kalman filtering, particle filtering, and Bayesian MCMC.}
        %\resumeItem{Emphasized robustness to persistence, misspecification, and measurement error.}
    \resumeItemListEnd
%\end{comment}

    \resumeSubheading{Dynamic Discrete Choice in Fast Food: Loyalty, Technology, \& Inequality}{Summer--Fall 2025}{Independent Research Project (with feedback from Prof. Amanda Smith)}{}
    \resumeItemListStart
        \resumeItem{Formulated and numerically optimized a structural model of discounts, channel choice (in-store vs. app vs. outside option), and loyalty adoption using exponential cone optimization (Julia/JuMP, MOSEK) with MNL demand.}
        
        \resumeItem{Built a reproducible simulation procedure (e.g., $T=20$) with evolving states, feasibility/termination checks, \& numerical stability via stable softmax. Outlined counterfactuals for COVID, input-cost inflation, inequality shocks.}
        
        \resumeItem{Ensured convexity despite MNL demand \& concave technology investment via log-sum-exp \& RSOC epigraphs. Avoided bilinearity by updating loyalty shares via lagged states. Added income segmentation via MILP Big-$M$.}
    \resumeItemListEnd

\begin{comment}
    \resumeSubheading{Experimental Design: The Rationality of the Poverty-Present Bias Connection}{Spring 2024}{Independent Research Paper (with feedback from Prof. David Hansen)}{}
    \resumeItemListStart

        \resumeItem{Designed a four-arm field experiment addressing spillovers, endogenous clustering, and attrition via baseline and attrition tests, ZIP-level randomization stratified by SPM area, and ACS-/SPM-based eligibility measures.}

        \resumeItem{Specified structural estimation of time preferences via generalized discounting models (exponential, hyperbolic, quasi-hyperbolic), logistic choice with noise, $J$-tests, and Wald tests for treatment effects on discounting.}

        \resumeItem{Wrote panel surveys of real-incentive intertemporal choice \& biomarkers (CES-D, PSS, WVS, salivary cortisol) and field implementation scripts (multilingual outreach, secure data intake, grievances, and debit-card disbursement). Developed a well-being index and precarity margin, and analyzed undercoverage of homelessness (e.g., PIT counts).}
    \resumeItemListEnd
\end{comment}

\begin{comment}
    \resumeSubheading{Thomas Piketty's \textit{Capital}: Theory, Empirics, Impact}{Fall 2023}{Research Paper}{}
    \resumeItemListStart
        \resumeItem{Unified a vast, diverse set of critiques (7 pages of references), contrasted alternative mechanisms (e.g., \href{https://doi.org/10.1093/qje/qjaa004}{superstar firms}), and highlighted data reliability issues while writing for a broad, non-econ audience.}
    \resumeItemListEnd
\end{comment}


\resumeSubHeadingListEnd

\vspace{-4mm}
%-----------WORK EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingListStart

%\begin{comment}    
    \resumeSubheading{Economic Consultant and Data Analyst: Capital and Firm Ownership in Retirement}{2024}{Maui Mastermind Business Coaching}{Remote}
    \resumeItemListStart

        \resumeItem{Harmonized SCF 2022 microdata with automated data integrity checks to characterize role of business ownership in post-retirement wealth persistence in R. Implemented survey design with 5 implicates, 999 replicate weights.}

        \resumeItem{Estimated age-grouped wealth distributions via survey-weighted quantiles (P50-P99.99) with replicate-weight SEs combined under multiple imputation. Illustrated and exported results in client-readable tables/figures.}

        \resumeItem{Produced breakdowns of asset/income composition (e.g., active/non-active business ownership) via nearest-neighbor selection by net worth for age$\times$percentile estimates. Detailed SCF measurement/sampling limitations, data gaps.}
        
    \resumeItemListEnd
%\end{comment}

    \resumeSubheading{Restaurant and Inventory Manager}{2022--2023}{Sookie’s Veggie Burgers}{Madison, WI}
    \resumeItemListStart
        \resumeItem{Built data-driven inventory tracker, cutting waste/holding times and building teamwork under stressful conditions.}
    \resumeItemListEnd

    \resumeSubheading{Tutor of College-Level Economics, Calculus, Chemistry, and US History}{2022--2023}{Self-Employed}{Remote}
    %\begin{comment}
    \resumeItemListStart
        \resumeItem{Improved student performance using self-made problem sets and exams, clear intuition, and engaging exposition.}
    \resumeItemListEnd
    %\end{comment}
\resumeSubHeadingListEnd

\vspace{-4mm}
%-----------EXTRACURRICULAR EXPERIENCE-----------
\section{Extracurricular Experience}
\resumeSubHeadingListStart

\vspace{0.5mm}

    \resumeSubheading{Policies for Labor Recovery: Economic Development Case Competition (\textit{\underline{1\textsuperscript{st} Place}})}{Fall 2024}{Sole Author of Written Report \& Collaborator on Presentation (with feedback from Prof. Simeon Alder)}{}
    \resumeItemListStart
        
        \resumeItem{Analyzed local general equilibrium impacts of a coal-plant closure using demand spillovers, labor reallocation, BLS and WI DWD projections, and direct/indirect/induced labor/fiscal losses  (\$251M output, \$2.8M taxes, 308 jobs).}
        
        \resumeItem{Designed demand-driven training addressing job-specific human capital, participation constraints (school funding, housing supply), and retention via supportive services (childcare, transportation) \& post-training mentorship guarantees. Evaluated funding constraints and alternatives beyond WIOA (e.g., WI Fast Forward, SCSEP).}
        
        \resumeItem{Presented strategies and potential partnerships for improving business dynamism and climate (licensing, zoning, knowledge diffusion) given local demand gaps (e.g., 50\% retail furniture leakage) to Alliant Energy, MadREP.}
        
    \resumeItemListEnd

\resumeSubheading{Presenter, \textnormal{PREDOC.org Research Conference}}{2026}{Booth School of Business, The University of Chicago}{}

\vspace{1mm}

\resumeSubheading{Presenter, \textnormal{Undergraduate Research Symposium}}{2025}{University of Wisconsin-Madison}{}

\begin{comment}
\vspace{1mm}

\resumeSubheading{Writer, \textnormal{Equilibrium: The Undergraduate Journal of Economics}}{2025}{Department of Economics, University of Wisconsin-Madison}{}
\end{comment}

\vspace{2.5mm}

\begin{comment}
\textbf{Further Leadership \& Outreach}: \small{Environmental Policy Organizing Team Lead (WSCAC), \\ Campaign Chair (ACLU-SA), Campaign Member (District 4 Elections)}
\end{comment}
\vspace{-1mm}


\resumeSubHeadingListEnd

\vspace{-4.5mm}
%-----------AWARDS AND HONORS-----------
\section{Awards \& Honors}
\resumeSubHeadingListStart

\vspace{0.5mm}

\resumeSubheading{Veldor Kopitzke Scholarship \textnormal{in Economics}}{Fall 2025}{Department of Economics, University of Wisconsin-Madison}{}

\vspace{1mm}

\resumeSubheading{Dean's List}{Fall 2023, Spring 2025, Spring 2026}{University of Wisconsin-Madison}{}

\vspace{2.5mm}

\textbf{Leadership Recognition}: \small{President’s Volunteer Service Award Winner (Field Museum),}\\ \small{Martin Luther King Jr. Outstanding Young Person Award (Urban League of Greater Madison), \\ Certificate of Distinguished Achievement for Outstanding Citizenship (American Legion)}

\resumeSubHeadingListEnd

\vspace{-5mm}
%-----------PROGRAMMING-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \item{
     \textbf{Proficient}{: R (incl. spdep), Python (incl. sklearn, transformers), Stata, Julia, MATLAB, SQL, Git, \LaTeX} \\
     \textbf{Familiar}{: C++, Fortran, JavaScript, HTML/CSS, Mathematica}
     }
 \end{itemize}


\end{document}